### 2019-02-20 manuscript/introduction.tex
- small intro change
- draft for Emma with everything but "Here, we..." paragraph

@@

Polyploidization alters the genomic content of all cells, and consequently has the potential to affect a wide variety, if not all, traits. 
From the very beginning, the study of this cytogenetic property considered correlations with other traits \citep{stebbins1938}. 
Among the many of changes associated with polyploidization, perhaps the most prominent is the association between polyploidy and propensity for self-fertilization \citep{stebbins1950, barrett1988}.
Polyploidy is not only a suspected correlate of breeding systems but a causal link \citep{stout1942, lewis1947}.
Doubled number of alleles in pollen is strongly suspected to effect disruption of the genetic mechanisms in gametophytic self-incompatibility systems \citep{entani1999, tsukamoto2005, kubo2010}. 
Polyploidy is also thought to be associated with changes in the rate of self-fertilization, although the evidence for this correlated shift in mating system appears limited and sometimes contradictory \citep{barringer2007, barrett2008, husband2008}.
Breeding system shifts---changes in the collection of physiological and morphological traits that determine the likelihood that any two gametes unite---are remarkably common and affect the distribution and amount of genetic variation in populations \citep{stebbins1974,barrett2013}.
They are by themselves thought to have a broad effect on other traits. 
The frequent transition from self-incompatibility (SI) to self-compatibility (SC) is strongly associated with net diversification rate changes \citep{goldberg_2010,devos2014}.
Given that  changes in ploidy and breeding systems may be causally related and have profound profound affects on the fate of lineages, it seems particularly profitable to examine whether and how their macroevolutionary effects interact.
%
% we also have this great data for SI loci and the transition could be even more common, providing power to resolve the great diversification questions
%
% set up pathway dependence

>>>>

%B: this is highly preliminary, for your editing consideration.
The systematic search for traits which influence the rates at which species accumulate around the tree of life is at the productive confluence of drastic increases in the size of datasets and equally dramatic improvements in analytical methods \citep{maddison_2007,fitzjohn_2009,goldberg_2012,beaulieu_2015}. % some papers with big trees.
Many limitations impede our progress in identifying estimating trait-dependent differences in speciation and extinction rates \citep{maddison_2015, rabosky_2015}. % add Moore/Hoehna?
Nevertheless, the field has made steady advances in relaxing assumptions and addressing conceptual difficulties. %maybe add beaulieu_2015 here, instead
One limitation is the pervasive consideration of traits in isolation. 
For example, studies commonly aim to identify the effects of alternate states of a single trait on the diversification process. 
This is problematic, because the context in which traits occur can lead to complex interactions, perhaps with other traits that make up an organism or its environment.
Consequently, an obvious direction for improvement of trait-dependent diversification models ought to involve development of approaches that allow investigation of individual and joint effects of traits on diversification, as well as each other's state transitions.
Ideally, the initial application of such approaches ought to rely on well-sampled and studied traits, whose interactions are relatively clear, and which show a wide phylogenetic distribution. 
%B: We can then have a good prior, reliable data, and replicate the studies.
In this paper, we use two of the best studied traits in flowering plants, ploidy and breeding system, and demonstrate an approach to consider their individual and joint effects on diversification.

@@

Polyploidization alters the genomic content of all cells, and consequently has the potential to affect a wide variety, if not all, traits. 
From the very beginning, the study of this cytogenetic property considered correlations with other traits \citep{stebbins1938}. 
Among the many of changes associated with polyploidization, perhaps the most prominent is the association between polyploidy and propensity for self-fertilization \citep{stebbins1950, barrett1988}.
Polyploidy is not only a suspected correlate of breeding systems but a causal link \citep{stout1942, lewis1947}.
Doubled number of alleles in pollen is strongly suspected to effect disruption of the genetic mechanisms in gametophytic self-incompatibility systems \citep{entani1999, tsukamoto2005, kubo2010}. 
Polyploidy is also thought to be associated with changes in the rate of self-fertilization, although the evidence for this correlated shift in mating system appears limited and sometimes contradictory \citep{barringer2007, barrett2008, husband2008}.

Breeding system shifts---changes in the collection of physiological and morphological traits that determine the likelihood that any two gametes unite---are remarkably common and affect the distribution and amount of genetic variation in populations \citep{stebbins1974,barrett2013}.
They are by themselves thought to have a broad effect on other traits. 
The frequent transition from self-incompatibility (SI) to self-compatibility (SC) is strongly associated with net diversification rate changes \citep{goldberg_2010,devos2014}.
Given that changes in ploidy and breeding systems may be causally related and have  profound affects on the fate of lineages, it seems particularly profitable to examine whether and how their macroevolutionary effects interact.
Moreover,  increases in ploidy are known to directly affect breeding system states and present a rare opportunity for the study of paths and path-dependence on trait evolution and diversification.
For example, we could ask if the ordinary mutation (and fixation) causes more losses of SI than polyploidization, whether more SC polyploids are generated directly, after polyploidization of diploid SI lineages, or through a two-step pathway, involving loss of SC and subsequent polyploidization of a SC lineage.
And, are diversification rates of polyploid SC lineages different if one or other path was taken? \citet{charlesworth1985} 
%
%trans-polymorphism: We also have this great data for SI loci and the transition could be even more common, providing power to resolve the great diversification questions
%
% set up pathway dependence from SI-D to SC-P: direct or via SC-D

Here, we [...]
% Someone else should do this, once we have the full data.
% diversification: interaction between ploidy and breeding system
% 	examine individual effects
% 	examine joint effects
% 	with and without HMMs
% 	allow for re-diploidization or not
% also: diploidization, pathways
% 	examine pathways from SI-D to SC-P: direct or via SC-D
